MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-28 paper.Rmd
Add acknowledgements.

@@

The new `R` packages

enables

@@

# Mathematics

Single dollars ($) are required for inline mathematics e.g. $f(x) = e^{\pi/x}$

Double dollars make self-standing equations:

$$\Theta(x) = \left\{\begin{array}{l}
0\textrm{ if } x < 0\cr
1\textrm{ else}
\end{array}\right.$$

You can also use plain \LaTeX for equations
\begin{equation}\label{eq:fourier}
\hat{f}(\omega) = \int_{-\infty}^{\infty} f(x) e^{i\omega x} dx
\end{equation}
and refer to \autoref{eq:fourier} from text.

# Figures

Figures can be included like this:

![Caption for example figure.\label{fig:example}](figure.png)
and referenced from text using \autoref{fig:example}.

Figure sizes can be customized by adding an optional second parameter:

![Caption for example figure.](figure.png){ width=20% }

>>>>

Create a MR-PFU database from the GHA and ZAF data contained in the IEATools package.
Create the expectd folder structure that we use on the database.
Store all necessary data in this repository.
Execute the commands to produce the database, 
albeit for only two countries and two years.

@@

The new `R` packages enable the creation of databases of primary, final, and useful stage
energy and exergy energy conversion chains.
Such databases will enable advances in societal exergy analysis community
and lead to greater insights on economic growth and human well-being.

<!-- # Mathematics -->

<!-- Single dollars ($) are required for inline mathematics e.g. $f(x) = e^{\pi/x}$ -->

<!-- Double dollars make self-standing equations: -->

<!-- $$\Theta(x) = \left\{\begin{array}{l} -->
<!-- 0\textrm{ if } x < 0\cr -->
<!-- 1\textrm{ else} -->
<!-- \end{array}\right.$$ -->

<!-- You can also use plain \LaTeX for equations -->
<!-- \begin{equation}\label{eq:fourier} -->
<!-- \hat{f}(\omega) = \int_{-\infty}^{\infty} f(x) e^{i\omega x} dx -->
<!-- \end{equation} -->
<!-- and refer to \autoref{eq:fourier} from text. -->

<!-- # Figures -->

<!-- Figures can be included like this: -->

<!-- ![Caption for example figure.\label{fig:example}](figure.png) -->
<!-- and referenced from text using \autoref{fig:example}. -->

<!-- Figure sizes can be customized by adding an optional second parameter: -->

<!-- ![Caption for example figure.](figure.png){ width=20% } -->

@@

MKH acknowledges the support of Calvin University for 
a sabbatical during which he developed the PSUT framework
and course releases during which he wrote many of the `R` packages
described in this paper.
ZM acknowledges ******. 
EA acknowledges ******.
PEB acknowledges ******.
